\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Shane J. Li} \\ \vspace{1pt}
    \small +1 (984) 999-8251 $|$ \href{mailto:juntao540@gmail.com}{\underline{shane.juntao.li@gmail.com}} $|$ 
    Chapel Hill, NC $|$
    \href{www.linkedin.com/in/shane-juntao-li}{\underline{www.linkedin.com/in/shane-juntao-li}} 
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{University of North Carolina - Chapel Hill}}{Aug 2023 -- Dec 2025}
    \resumeItemListStart
      \resumeItem{Bachelor's in Computer Science, GPA: 3.8/4.0}
      \resumeItem{Relevant coursework: Data Structures \& Algorithms, Operating Systems, Systems Programming, Computer Organization, Cryptography, Models of Computation}
      \resumeItem{Supporting math coursework: Differential Equations, Probability, Applied Calculus}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeProjectHeading
          {\textbf{PMG} $|$ \emph{Software Engineer}}{Jan 2026 -- Present}
          \resumeItemListStart
            \resumeItem{Built a MCP Slack bot using Python with FastAPI to automate channel creation and built sematic layer from Alli Data for easy access of company knowledge, reducing manual setup time for 5 cross-functional teams.}
            \resumeItem{Designed and implemented LLM-powered workflow to detect market culture sentiment, automating manual analysis processes and processing 500+ data points daily to identify emerging trends through News API.}
            \resumeItem{Full-stack development in Creative Studio with React and Django, used Celery with AWS SQS as the broker for media management systems, and AWS S3 \& ECS for digital asset storage and workflows.}
    \resumeItemListEnd
  \resumeProjectHeading
    {\textbf{Arch Capital Group} $|$ \emph{Software Development \& Architect Intern}}{Jun 2025 -- Dec 2025}
    \resumeItemListStart
      \resumeItem{Built and refactored 6+ Spring Boot API endpoints and resolved 3+ backend defects by integrating with internal systems like Guidewire, RMA, and ElasticSearch with other data in MySQL Database.}
      \resumeItem{Integrated AWS Bedrock with Claude model to implement LLM-powered capabilities, enhancing application functionality with AI-driven features on AWS cloud infrastructure.}
      \resumeItem{Deployed 5+ docker images daily using Github actions with kubernetes and Terraform configurations for feature and defect testing. Published 4+ Confluence technical writings for troubleshooting and solution design. }
      \resumeItem{Enhanced Angular (TypeScript + NodeJS) UI with 40+ unit/integration tests utilizing containerization and CI/CD workflow in software development lifecycle. }
    \resumeItemListEnd



  \resumeProjectHeading
    {\textbf{UNC Charlotte} $|$ \emph{Research Assistant}}{Sep 2022 -- Jul 2023}
    \resumeItemListStart
      \resumeItem{Implemented advanced privacy protocols (RAPPOR, LDP, ULDP) improving effectiveness by 30\% using large datasets.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart


  \resumeProjectHeading
  {\textbf{\href{https://apps.microsoft.com/detail/9pcj0v1kcswm?hl=en-US\&gl=US}{RNG Capitalist}} $|$ \emph{Flutter/Dart, Cross-Platform}}{Chapel Hill, NC}
    \resumeItemListStart
      \resumeItem{Developed a cross-platform productivity tool that schedules tasks based on past spending decisions using behavioral economics principles.}
      \resumeItem{Implemented in Flutter/Dart with full desktop and mobile support.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{\href{https://ecosprout.fun/}{EcoSprout}} $|$ \emph{Software Front-end}}{Chapel Hill, NC}
    \resumeItemListStart
      \resumeItem{Architected a React 18 single-page application with home, tutorial, single-player, and multiplayer modes featuring neighbor-based crop combat, randomized weather, and an inventory-driven market economy.}
      \resumeItem{Extended functionality into a turn-based competitive mode with per-tile ownership, rain-boosted growth, win condition enforcement, and dynamically styled player-branded boards.}
    \resumeItemListEnd
\resumeProjectHeading
  {\textbf{\href{https://cerrig.pro/}{Cerrig.pro}} $|$ \emph{WordPress, Web Development}}{Chapel Hill, NC}
\resumeItemListStart
  \resumeItem{Built and launched a fully functional professional website independently using WordPress, handling both design and development.}
  \resumeItem{Customized themes, plugins, and site architecture to create a responsive, user-friendly experience optimized for both desktop and mobile.}
  \resumeItem{Managed deployment, content integration, and SEO optimization to ensure visibility and performance.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Languages}{: Java, Python, TypeScript, JavaScript, C, C++, SQL, HTML/CSS, MATLAB} \\
   \textbf{Frameworks/Tools}{: React.js, Flask, Spring Boot, Docker, Git, AWS, Linux/Unix, MySQL, Agile, DevOps} \\
   \textbf{Other}{: Networking, Data Science, Project Management, Test Automation, System Integration, Troubleshooting}
  }}
\end{itemize}

\end{document}
